Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Final State with Multivariate Techniques

### 2015-12-23 paper/sec-analysis.tex
updated plots with trimming

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
  \includegraphics[width=0.63\textwidth]{plots/m_htot_res_signal_PUnoSK.pdf}
    \caption{\small
    The invariant mass distributions of Higgs candidates in signal
events in the resolved category, comparing the results without PU,
with PU $\la n_{\rm PU}\ra=80$. The distribution is then compared with and without SK subtraction.
}
\label{fig:PUvalidation}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

To validate the subtraction of PU,
we compare representative kinematic distributions
without PU, with PU, and with PU after SK subtraction.
%
In Fig.~\ref{fig:PUvalidation} we show the
invariant mass distributions of Higgs candidates for signal
events in the resolved category.
%
If PU is not subtracted there is a large shift in the Higgs mass
peak, by about 40 GeV.
%
Once SK subtraction is performed, we recover a distribution much closer
to the no PU case, with only a small shift of $\simeq 5$ GeV
and a broadening of the mass
distribution.
%

In Fig.~\ref{fig:m_H_PU} we show the invariant mass distribution
of the leading and subleading Higgs candidates,
this time corresponding
to the boosted category.
%
These distributions are plotted
after
$b$-tagging, that is,
before they are used as input to the MVA.
%
The residual effects of PU
after the {\tt SoftKiller} subtraction are smaller
in the boosted selection as compared to the resolved case,
with the position of the Higgs mass peak being essentially
unchanged, and only a moderate broadening of the
mass distribution.
%

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
      \includegraphics[width=0.49\textwidth]{plots/m_H0_bst_comp.pdf}
      \includegraphics[width=0.49\textwidth]{plots/m_H1_bst_comp.pdf}
  \caption{\small
    Comparison of the invariant mass distributions of the leading (left)
    and subleading (right) Higgs candidates
    in the boosted category,
    both without PU and with
    PU, $\la n_{PU}\ra=80$, subtracted by {\tt SoftKiller}.
}
\label{fig:m_H_PU}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
  \includegraphics[width=0.49\textwidth]{plots/pt_H0_C2_res_comp.pdf}
  \includegraphics[width=0.49\textwidth]{plots/pt_H0_C2_bst_comp.pdf}
  \includegraphics[width=0.49\textwidth]{plots/m_HH_C2_res_comp.pdf}
  \includegraphics[width=0.49\textwidth]{plots/m_HH_C2_bst_comp.pdf}
  \caption{\small
    Same as Fig.~\ref{fig:m_H_PU} for
   the transverse momentum $p_T^h$ of the leading
    Higgs candidate (upper plots) and of the invariant mass $m_{hh}$
    of the di-Higgs system (lower plots) in the resolved
    (left) and boosted (right) categories.
}
\label{fig:mHH_PU}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

We can also assess the impact of PU in some of
substructure variables that will be 
used as input to the MVA in the boosted category.
%
In Fig.~\ref{fig:Substructure_PU} we show the 2-to-1 subjettiness ratio
$\tau_{21}$, Eq.~(\ref{eq:tau21}), and the ratio
of energy correlation functions, $D_2^{(\beta)}$,
Eq.~(\ref{eq:d2}), for the leading Higgs candidate.
%
Comparing the signal distributions in the cases without PU and
with PU subtracted with SK, we observe that both substructure variables
are reasonably robust in a environment including PU.
%
The ratio of energy correlation functions $D_2^{(\beta)}$ 
was indeed explicitly constructed~\cite{Larkoski:2013eya}
to be robust against PU contamination.
%

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
  \includegraphics[width=0.49\textwidth]{plots/D2_h0_bst_comp.pdf}
  \includegraphics[width=0.49\textwidth]{plots/tau21_h0_bst_comp.pdf}
  \caption{\small
    Same as Fig.~\ref{fig:m_H_PU} for the
    substructure variables $D_2^{(\beta)}$ (left)
     and $\tau_{21}$ (right)
     for the leading Higgs candidates in the boosted category.
}
\label{fig:Substructure_PU}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
  \includegraphics[width=0.49\textwidth]{plots/pt_h0_bst_comp_back.pdf}
   \includegraphics[width=0.49\textwidth]{plots/tau21_h1_bst_comp_back.pdf}
   \includegraphics[width=0.49\textwidth]{plots/split12_h0_bst_comp_back.pdf}
   \includegraphics[width=0.49\textwidth]{plots/m_h0_bst_comp_back.pdf}
   \caption{\small
     Comparison of kinematic distributions, in
     the boosted category, for signal and background events
    in the case of PU subtracted with SK:
     the transverse momentum  $p_T$ and
     and the substructure variables $\tau_{21}$ and $\sqrt{d_{12}}$
     for the leading Higgs candidate, and the invariant
     mass of the di-Higgs system $m_{hh}$.
     %
 }
\label{fig:signal-vs-back-boosted}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

We can also perform a similar comparison for
the resolved category.
%
In Fig.~\ref{fig:signal-vs-back-resolved} we compare
the kinematic distributions for signal and background events,
     with and without PU, for the invariant mass and the $p_T$ of the leading
     Higgs candidate.
     %
%     Also in this
%     case
Again, the PU-subtracted background distributions appear reasonably close
     to their no PU counterparts.

@@

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{table}[h]
      \centering
      \begin{tabular}{|c|c|c|c|}
        \hline
        \multicolumn{4}{|c|}{Resolved category}\\
        \hline
        \hline
        &   &   $\la m_h^{\rm reco}\ra-m_h$  &  $\sigma_{m_h}$  \\
              \hline
        \multirow{2}{*}{no PU}  & leading Higgs  &  -3.8 GeV   & $\lp 8.5\pm 0.2\rp$ GeV   \\
          & subleading Higgs   & -5.8 GeV  &  $\lp 9.1\pm 0.3\rp$ GeV \\
        \hline
          \multirow{2}{*}{$\la n_{\rm PU}\ra=80$}  & leading Higgs  &  +33 GeV   & $\lp 8.8\pm 1.5\rp$ GeV   \\
          & subleading Higgs   & +31 GeV  &  $\lp 11.7\pm 3.3\rp$ GeV \\
          \hline
            \multirow{2}{*}{$\la n_{\rm PU}\ra=80$+SK}  & leading Higgs  &  +3.9 GeV   & $\lp 10.7\pm 0.3\rp$ GeV   \\
          & subleading Higgs   & +2.1 GeV  &  $\lp 10.5\pm 0.3\rp$ GeV \\
            \hline
            \multicolumn{4}{c}{}\\
             \hline
        \multicolumn{4}{|c|}{Boosted category}\\
        \hline
        \hline
        &   &   $\la m_h^{\rm reco}\ra-m_h$  &  $\sigma_{m_h}$  \\
              \hline
        \multirow{2}{*}{no PU}  & leading Higgs  &  +2 GeV   & $\lp 8.2\pm 0.5\rp$ GeV   \\
          & subleading Higgs   & +1 GeV  &  $\lp 8.8\pm 0.5\rp$ GeV \\
        \hline
              \multirow{2}{*}{$\la n_{\rm PU}\ra=80$+SK}  & leading Higgs  &  --   & --   \\
          & subleading Higgs   & --  &  -- \\
        \hline
        \end{tabular}
      \caption{\label{tab:massresolution}
        Resolution of the invariant mass distribution of
        reconstructed Higgs candidates in the resolved (upper table)
        and boosted (categories) category.
        %
        We show three cases: without PU, with PU $\la n_{\rm PU}\ra=80$
        but without subtraction, and the same with SK subtraction.
        %
        We indicate the shift of the invariant
        mass peak $\la m_h^{\rm reco}\ra$ as compared
        to the nominal Higgs mass $m_h=125$ GeV, as well as the width
        of a Gaussian fitted to the mass distribution, $\sigma_{m_h}$,
        for both the leading and subleading Higgs candidates.
      }
      \end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

In addition, trimming~\cite{Krohn:2009th}, as implemented in {\tt FastJet}, is applied to all large-$R$ jets in the event.
%
The trimming parameters are chosen such that the constituents of a given jet are reclustered into $k_T$~\cite{Ellis:1993tq} 
subjets with $R_{\textrm{sub}} = 0.2$.
Subjets with transverse momentum less than 5\% of the transverse momentum of the large-$R$ jet are removed.
%
The use of trimming in addition to PU removal with {\tt SoftKiller} is necessary to correct the jet mass in the boosted category,
which is particularly susceptible
to soft, wide-angle contaminations.
%
No trimming is applied to the small-$R$ jets.

To validate the subtraction of PU,
we compare representative kinematic distributions
without PU, with PU, and with PU after the combined
application of {\tt SoftKiller} and trimming (SK+Trim).
%
In Fig.~\ref{fig:PUvalidation} we show the
invariant mass distributions of the
Higgs candidates for signal
events in the resolved and boosted categories.
%
If PU is not subtracted there is a large shift in the Higgs mass
peak, by about 40 GeV.
%
Once SK subtraction is performed, we recover a distribution much closer
to the no PU case, with only a small shift of $\simeq 5$ GeV
and a broadening of the mass
distribution.
%
For the boosted category, we find that
the mass distributions for jets to which no trimming
is applied peaks at around 160~GeV, even
after PU subtraction with {\tt SoftKiller}.
%
When trimming is applied in addition to {\tt SoftKiller}, 
the distribution peaks close to the nominal Higgs mass.

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.49\textwidth]{plots/m_htot_res_signal_PUnoSK.pdf}
    \includegraphics[width=0.49\textwidth]{plots/m_htot_bst_signal_PUnoTrim.pdf}
    \caption{\small
    The invariant mass distributions of Higgs candidates in signal
    events in the resolved (left) and boosted
    (right) categories.
    %
    In the resolved category,
    we compare  the results without PU
    with those with PU $\la n_{\rm PU}\ra=80$,
    with and without SK subtraction.
    %
    In the boosted case, the comparison is between no PU,
    PU with only SK subtraction,
    and PU with both SK and trimming.
}
\label{fig:PUvalidation}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
  \includegraphics[width=0.49\textwidth]{plots/pt_H0_C2_res_comp.pdf}
  \includegraphics[width=0.49\textwidth]{plots/pt_H0_C2_bst_comp.pdf}
  \includegraphics[width=0.49\textwidth]{plots/m_HH_C2_res_comp.pdf}
  \includegraphics[width=0.49\textwidth]{plots/m_HH_C2_bst_comp.pdf}
  \caption{\small
   The
   transverse momentum $p_T^h$ of the leading
    Higgs candidate (upper plots) and of the invariant mass $m_{hh}$
    of the di-Higgs system (lower plots) in the resolved
    (left) and boosted (right) categories.
    %
    We compare the results without PU with those with PU,
    for $\la n_{\rm PU}\ra=80$ and SK+Trim subtraction,
    as explained in the text.
}
\label{fig:mHH_PU}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

We can also assess the impact of PU in some of
substructure variables that will be 
used as input to the MVA in the boosted category.
%
In Fig.~\ref{fig:Substructure_PU} we show the 2-to-1 subjettiness ratio
$\tau_{21}$, Eq.~(\ref{eq:tau21}), and the ratio
of energy correlation functions, $C_2^{(\beta)}$,
Eq.~(\ref{eq:c2}), for the leading Higgs candidate.
%
Comparing the signal distributions in the cases without PU and
with PU subtracted with SK, we observe that
the shapes of both substructure variables
are reasonably robust in a environment including PU.
%

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.49\textwidth]{plots/tau21_h0_bst_comp.pdf}
  \includegraphics[width=0.49\textwidth]{plots/D2_h0_bst_comp.pdf}
    \caption{\small
    Same as Fig.~\ref{fig:mHH_PU} for the
    substructure variables $\tau_{21}$  (left)
     and  $C_2^{(\beta)}$ (right)
     for the leading Higgs candidates in the boosted category.
}
\label{fig:Substructure_PU}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.49\textwidth]{plots/pt_h0_bst_comp_back.pdf}
    \includegraphics[width=0.49\textwidth]{plots/pt_leadSJ_fj1_bst_comp_back.pdf}
   \includegraphics[width=0.49\textwidth]{plots/tau21_h1_bst_comp_back.pdf}
   \includegraphics[width=0.49\textwidth]{plots/split12_h0_bst_comp_back.pdf}
    \caption{\small
      Comparison of kinematic distributions for the leading
      Higgs candidate, in
     the boosted category, for signal and background events
    in the case of PU subtracted with SK+Trim:
    its transverse momentum  $p_T$,
    the $p_T$ of its leading AKT03 subjet,
    and the substructure variables $\tau_{21}$ and $\sqrt{d_{12}}$.
  }
\label{fig:signal-vs-back-boosted}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

We can also perform a similar comparison for
the resolved category.
%
In Fig.~\ref{fig:signal-vs-back-resolved} we compare
the kinematic distributions for signal and background events,
     with and without PU, for the invariant mass and the $p_T$ of the leading
     Higgs candidate.
     %
Again, the PU-subtracted background distributions appear reasonably close
     to their no PU counterparts.

@@

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{table}[h]
      \centering
      \begin{tabular}{|c|c|c|c|}
        \hline
        \multicolumn{4}{|c|}{Resolved category}\\
        \hline
        \hline
        &   &   $\la m_h^{\rm reco}\ra-m_h$  &  $\sigma_{m_h}$  \\
              \hline
        \multirow{2}{*}{no PU}  & leading Higgs  &  -3.8 GeV   & $\lp 8.5\pm 0.2\rp$ GeV   \\
          & subleading Higgs   & -5.8 GeV  &  $\lp 9.1\pm 0.3\rp$ GeV \\
        \hline
          \multirow{2}{*}{$\la n_{\rm PU}\ra=80$}  & leading Higgs  &  +33 GeV   & $\lp 8.8\pm 1.5\rp$ GeV   \\
          & subleading Higgs   & +31 GeV  &  $\lp 11.7\pm 3.3\rp$ GeV \\
          \hline
            \multirow{2}{*}{$\la n_{\rm PU}\ra=80$+SK}  & leading Higgs  &  +3.9 GeV   & $\lp 10.7\pm 0.3\rp$ GeV   \\
          & subleading Higgs   & +2.1 GeV  &  $\lp 10.5\pm 0.3\rp$ GeV \\
            \hline
            \multicolumn{4}{c}{}\\
             \hline
        \multicolumn{4}{|c|}{Boosted category}\\
        \hline
        \hline
        &   &   $\la m_h^{\rm reco}\ra-m_h$  &  $\sigma_{m_h}$  \\
              \hline
        \multirow{2}{*}{no PU}  & leading Higgs  &  +2.0 GeV   & $\lp 8.2\pm 0.5\rp$ GeV   \\
          & subleading Higgs   & +1.0 GeV  &  $\lp 8.8\pm 0.5\rp$ GeV \\
        \hline
              \multirow{2}{*}{$\la n_{\rm PU}\ra=80$+SK+Trim}  & leading Higgs  &  -2.2 GeV   & $\lp 8.7\pm 0.7\rp$ GeV   \\
          & subleading Higgs   & -4.9 GeV  &  $\lp 9.0\pm 0.8 \rp$ GeV \\
        \hline
        \end{tabular}
      \caption{\label{tab:massresolution}
        Resolution of the invariant mass distribution of
        reconstructed Higgs candidates in the resolved (upper table)
        and boosted (categories) category.
        %
        We show three cases: without PU, with PU $\la n_{\rm PU}\ra=80$
        but without subtraction (only for resolved),
        and the same with SK(+Trim) subtraction.
        %
        We indicate the shift of the invariant
        mass peak $\la m_h^{\rm reco}\ra$ as compared
        to the nominal Higgs mass $m_h=125$ GeV, as well as the width
        of a Gaussian fitted to the mass distribution, $\sigma_{m_h}$,
        for both the leading and subleading Higgs candidates.
      }
    \end{table}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
